### 2019-04-09 initial/notes.tex
EOM seems to be correct
foo

>>>>

\subsection{Equation of Motion}

The correct EOM comes from Kassandra's Eq.\ 12:
\begin{align*}
    \rd{\hat{s}}{t} ={}&
        \p*{\hat{s} \cdot \hat{l}}\p*{\hat{s} \times \hat{l}}
            -\eta\p*{\hat{s} \times \hat{l}_p},\\
        ={}& \cos\theta \s*{
            \hat{x}\p*{-\sin\theta \sin\phi}
            - \hat{y}\p*{-\sin\theta \cos\phi}}\\
            &- \eta \s*{
                \hat{x}\p*{-\sin\theta \sin \phi \cos I}
                - \hat{y}\p*{-\sin \theta \cos \phi \cos I
                    - \cos \theta\sin I}
                + \hat{z}\p*{+\sin\theta \sin \phi \sin I}},\\
        ={}& \s*{-\sin\theta \sin\phi \cos\theta
            + \eta \sin \theta \sin \phi \cos I}\hat{x}
            + \s*{\cos\theta \sin\theta \cos\phi
                - \eta\p*{\sin\theta \cos\phi \cos I
                    + \cos\theta \sin I}}\hat{y}\\
            &+ \s*{-\eta\sin\theta \sin\phi \sin I}\hat{z}.
\end{align*}

Alternatively, consider Hamilton's equations applied to the Hamiltonian:
\begin{align}
    \pd{\phi}{t} = \pd{\mathcal{H}}{(\cos\theta)}
        &= \cos\theta - \eta\p*{\cos I + \sin I \cot \theta \cos \phi},\\
    \pd{(\cos \theta)}{t} = -\pd{\mathcal{H}}{\phi}
        &= +\eta \sin I \sin \theta \sin \phi.
\end{align}
This seems to produce the same trajectories as Kassandra's EOM\@!

We can check the stability of each of the equilibria of the EOM, there should be
four corresponding to the four Cassini states:
